Language-Based Security for Low-Level MPC

### 2024-05-18 ppdp24/model.tex
checkpoint

Our semantics require that random tapes contain values for all program
values $\elab{\flip{w}}{\cid}$ sampled from a uniform distribution
over $\mathbb{F}_p$. Input memories also contain input secret values
and possibly other initial view elements as a result of
pre-processing, e.g., Beaver triples for efficient multiplication,
and/or MACed share distributions as in SPDZ \cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3}.
We will also assume that any possible initial secrets are equally
likely when formulating the program distribution.  We define
$\runs(\prog)$ as the set of final memories resulting from execution
of $\prog$ given any initial memory, and treat all elements of
$\runs(\prog)$ as equally likely.  This establishes the basic program
distribution that can be marginalized and conditioned to quantify
input/output information dependencies.
%In this
%setting, given a program $\prog$ with $\iov(\prog) = S \cup V$ and
%$\flips(\prog) = F$ we will consider all $\store \in \mems(S \cup V
%\cup F)$ such that $ \config{\store_{S \cup F}}{\prog} \redxs
%\config{\store_}{\varnothing} $ to be equally probable, establishing
%the basic distribution of the program. %From this, we can immediately
%derive the marginal distribution of $S \cup V$ to reason about
%dependencies between secrets and views.
\begin{definition}
  \label{def-progtt}
  \label{def-progd}
  \label{definition-progd}
  Given $\prog$ with $\secrets(\prog) = S$ and $\flips(\prog) = R$ and
  pre-processing predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \runs(\prog) \defeq \\
    \{ \store \mid \exists \store_1 \in \mems(R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \cap \store_2,\prog) \redxs (\store,\varnothing) \}
  \end{array}
  $$
  By default, $\preproc(\store) \iff \dom(\store) = S$, i.e.,
  the initial memory contains all input secrets in a uniform
  marginal distribution. Then the \emph{basic distribution of $\prog$}, written $\progtt(\prog)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\store) =  1 / |\runs(\prog)| \ \text{if}\ \store \in \runs(\prog), \text{otherwise}\ 0
  $$

>>>>

Our semantics require that random tapes contain values for all program
values $\elab{\flip{w}}{\cid}$ sampled from a uniform distribution
over $\mathbb{F}_p$. Input memories also contain input secret values
and possibly other initial view elements as a result of
pre-processing, e.g., Beaver triples for efficient multiplication,
and/or MACed share distributions as in BDOZ/SPDZ
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3}.  We will also
assume that any possible initial secrets are equally likely when
formulating the program distribution.  We define $\runs(\prog)$ as the
set of final memories resulting from execution of $\prog$ given any
initial memory, and treat all elements of $\runs(\prog)$ as equally
likely.  This establishes the basic program distribution that can be
marginalized and conditioned to quantify input/output information
dependencies.
%In this
%setting, given a program $\prog$ with $\iov(\prog) = S \cup V$ and
%$\flips(\prog) = F$ we will consider all $\store \in \mems(S \cup V
%\cup F)$ such that $ \config{\store_{S \cup F}}{\prog} \redxs
%\config{\store_}{\varnothing} $ to be equally probable, establishing
%the basic distribution of the program. %From this, we can immediately
%derive the marginal distribution of $S \cup V$ to reason about
%dependencies between secrets and views.
\begin{definition}
  \label{def-progtt}
  \label{def-progd}
  \label{definition-progd}
  Given $\prog$ with $\secrets(\prog) = S$ and $\flips(\prog) = R$ and
  pre-processing predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \runs(\prog) \defeq \\
    \{ \store \mid \exists \store_1 \in \mems(R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \cap \store_2,\prog) \redxs (\store,\varnothing) \}
  \end{array}
  $$
  By default, $\preproc(\store) \iff \dom(\store) = S$, i.e.,
  the initial memory contains all input secrets in a uniform
  marginal distribution. Then the \emph{basic distribution of $\prog$}, written $\progtt(\prog)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\store) =  1 / |\runs(\prog)| \ \text{if}\ \store \in \runs(\prog), \text{otherwise}\ 0
  $$
